Article Title

### 2013-10-16 sections/Simulation.tex

A common misconception about regularization is that its effect depends on accurate prior knowlege about the structure of the data. However, substantial improvement can be attained by shrinking the unbiased estimate toward an arbitrary target as long as the target is less variable than the unbiased estimator.  This unintuitive phenomenon is known as \emph{Stein's phenomenon} or \emph{Stein's paradox} \cite{Efron:1977} named after its discoverer Charles Stein \cite{Stein:1956}.
The more accurate description of regularization is as of the optimal tradeoff between estimation and approximation error, the so-called ``bias-variance tradeoff'' as described in earlier sections. 
Taken in isolation, the fact that a given regularized estimator improves the estimate should not be interpreted to suggest that its target estimate has the same low-dimensional structure as the data generating process.   However, when multiple estimators are compared against each other, the ones whose target estimate can closely approximate the true value with the smallest number of parameters will be able to reduce the estimation error with mininimum increases in approximation error when compared against other estimators whose targets cannot consistenly approximate the true covariance matrix.

To illustrate the convergence of the four regularized covariance matrix estimators,  we constructed several kinds of covariance matrices to be used as the true covariance matrices for multivariate normal distributions to be used in simulations studies. Four of such true matrices, sized $100\times100$ are shown in Fig.~\ref{fig:03} A--D.  It is computed as the sample covariance matrix of a finite sample (n=1000) drawn from a multivariate normal distribution with independent units and unit variances.  True matrix A has no low-dimensional structure: it takes $p\times(p+1)/2=5,050$ parameters to be fully defined.  True matrix B is computed by factor analysis from matrix A with $d=6$ factors.  As such, it has a low dimensional structure: it is fully defined with $p\times d +p = 700$ parameters.  True matrix C is computed by reducing to zero a large fraction the coefficients of the inverse of true matrix A \TODO{using GLASSO}. In this instance, 64.6\% of its off-diagonal elements are zero, and the entire matrix is fully defined with 1,825 parameters. Finally, true matrix D is an approximation of $A$ such that its inverse is a sum of a sparse matrix (74.1\% zeros of the digonal) and a low-rank component with rank $d=3$, with the number of parameters totaling 1582.

>>>>

A common misconception about regularization is that its effect depends on accurate prior knowlege about the structure of the data. However, substantial improvement can be attained by shrinking the unbiased estimate toward an arbitrary target as long as the target is less variable than the unbiased estimator.  This counter--intuitive phenomenon is known as \emph{Stein's phenomenon} or \emph{Stein's paradox} \cite{Efron:1977} named after its discoverer Charles Stein \cite{Stein:1956}.
The more accurate description of regularization is as of the optimal tradeoff between estimation and approximation error, the so-called ``bias-variance tradeoff'' as described in earlier sections. 
Taken in isolation, the fact that a given regularized estimator improves the estimate should not be interpreted to suggest that its target estimate has the same low-dimensional structure as the data generating process.   However, when multiple estimators are compared against each other, the ones whose target estimate can closely approximate the true value with the smallest number of parameters will be able to reduce the estimation error with mininimum increases in approximation error when compared against other estimators whose targets cannot consistenly approximate the true covariance matrix. 
\Kcomment{This seems a bit too wordy for the main part of the text.  I think the same can be said in a couple sentences.
People will likely wonder what this has to do with the analysis you are doing, if you spend too much time on generalities.}

To illustrate the convergence of the four regularized covariance matrix estimators,  we constructed several kinds of covariance matrices to be used as the true covariance matrices for multivariate normal distributions to be used in simulations studies. Four of such true matrices, sized $100\times100$ are shown in Fig.~\ref{fig:03} A--D.  \Kcomment{What does the ``It'' in the following part of the text refer to?  Do you mean ``Each''?} It is computed as the sample covariance matrix of a finite sample (n=1000) drawn from a multivariate normal distribution with independent units and unit variances.  True matrix A has no low-dimensional structure: it takes $p\times(p+1)/2=5,050$ parameters to be fully defined.  True matrix B is computed by factor analysis from matrix A with $d=6$ factors.  As such, it has a low dimensional structure: it is fully defined with $p\times d +p = 700$ parameters.  True matrix C is computed by reducing to zero a large fraction the coefficients of the inverse of true matrix A \TODO{using GLASSO}. In this instance, 64.6\% of its off-diagonal elements are zero, and the entire matrix is fully defined with 1,825 parameters. Finally, true matrix D is an approximation of $A$ such that its inverse is a sum of a sparse matrix (74.1\% zeros of the digonal) and a low-rank component with rank $d=3$, with the number of parameters totaling 1582.
